A weakly structured stem for human origins in Africa

### 2022-03-01 paper.tex
more edits, Caption to figure 2

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/fig2}
    \caption{
        \textbf{A weakly structured stem leads to best-fitting models}
        In the two best-fitting parameterizations of early population structure,
        continuous migration (A) and multiple mergers (B), models
        that include ongoing migration between stem populations outperform
        those in which stem populations are isolated. Most recent populations are
        connected by continuous, reciprocal migration that are indicated by 
        double-headed arrows (labels matched to migration rates and divergence
        times in Table~\ref{tab:migration-rates}). These migrations last for the
        duration of concurrence \sgcomment{concurrence or co-occurence? What does this mean in either case?} of contemporaneous populations \sgcomment{Is what we mean: Migration rates are constant over epochs delimited by population splits or mergers, see Supplementary table XX? }. The
        merger-with-stem-migration model (B) outperformed the
        continuous-migration model (A), $LL=-102,600$ vs $-115,500$,
        respectively.
    }
    \label{fig:2}
\end{figure}

>>>>

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/fig2}
    \caption{
        \textbf{A weakly structured stem best describes two-locus statistics}
        In the two best-fitting parameterizations of early population structure,
        continuous migration (A) and multiple mergers (B), models
        that include ongoing migration between stem populations outperform
        those in which stem populations are isolated. Most recent populations are
        connected by continuous, reciprocal migration that are indicated by 
        double-headed arrows (labels matched to migration rates and divergence
        times in Table~\ref{tab:migration-rates}). These migrations last for the
        duration of concurrence \sgcomment{concurrence or co-occurence? What does this mean in either case?} of contemporaneous populations \sgcomment{Is what we mean: Migration rates are constant over epochs delimited by population splits or mergers, see Supplementary table XX? }. The
        merger-with-stem-migration model (B, with  $LL=-102,600$) outperformed the
        continuous-migration model (A, with $LL=-115,500$ ).
    }
    \label{fig:2}
\end{figure}
